---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# genekitr

**genekitr** is an R analysis toolkit based on the gene. It mainly contains five features:

- Search: Gene IDs as input then get gene-related information (exp. location, gene name, gene alias, GC content ...) as well as search gene-related PubMed records

- Transform: Transform gene ID type among "symbol", "entrezid", "ensembl" and "uniprot"

- Analysis: Gene enrichment analysis including ORA (GO and KEGG) and GSEA

- Visualize: Visualization for enrichment analysis and gene overlaps

- Export: Gene IDs and analysis results could be exported as various sheets in one Excel file, which could be easily read and shared with others

**Why develop this R package?**


用户痛点：

- ID转换不够全，很多gene alias 不能够被识别（比如huamn 的BCC7实际对应TP53，mouse的Tp53实际可能对应Trp53, Trp53inp2 & Ano9）

- 参数设置不够友好，太繁琐（我们允许用户只输入基因id，至于它是symbol、entrez还是其他，函数可以自行判断）

- 保持和数据库的同步（ensembl、Uniprot），很多MassSpec数据中uniprot ID对应的symbol存在错误或者不完整，我们可以尽量减少

- ...


## Table of Contents

* [Installation](#installation)
* [Quick guide](#quick-guide)
* [Vignette](#vignette)
* [Citation](#citation)
* [Welcome to contribute](#welcome-to-contribute)

## Installation

Install CRAN stable version:

```{r, eval=FALSE}
install.packages("genekitr")
```

Install GitHub dev version:

```{r install-github, eval = FALSE}
# install.packages("remotes")
remotes::install_github("GangLiLab/genekitr")
# To build local vignette:
# remotes::install_github("GangLiLab/genekitr", build_vignettes = TRUE, dependencies = TRUE)
```

## Quick guide




## Vignette




## Citation

Wait for paper ...


## Welcome to contribute

If you are interested in this tool, welcome contribute your ideas as follows:

* Git clone this project
* Double click `genekitr.Rproj` to open RStudio
* Modify source code in `R/` folder
* Run `devtools::check()` to make sure no errors, warnings or notes
* Pull request








