---
title: "genekitr: an R toolkit for gene-based analysis"
author: "Yunze Liu \\
        University of Macau"
date: "`r Sys.Date()`"

output:
  prettydoc::html_pretty:
    toc: true
    theme: cayman
    highlight: github
  pdf_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{Basic usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

**genekitr** is an R analysis toolkit based on the gene. It mainly contains five features:

- Search: Gene IDs as input then get gene-related information (exp. location, gene name, gene alias, GC content ...) as well as search gene-related PubMed records

- Transform: Transform gene ID type among "symbol", "entrezid", "ensembl" and "uniprot"

- Analysis: Gene enrichment analysis including ORA (GO and KEGG) and GSEA

- Visualize: Visualization for enrichment analysis and gene overlaps

- Export: Gene IDs and analysis results could be exported as various sheets in one Excel file, which could be easily read and shared with others

## Installation

Install CRAN stable version:

```{r, eval=FALSE}
install.packages("genekitr")
```

Install GitHub dev version:

```{r install-github, eval = FALSE}
# install.packages("remotes")
remotes::install_github("GangLiLab/genekitr")
# To build local vignette:
# remotes::install_github("GangLiLab/genekitr", build_vignettes = TRUE, dependencies = TRUE)
```

## Usage

```{r DT_opt, include=FALSE}
options(DT.options = list(pageLength = 3, 
                          language = list(search = 'Filter:'),
                          autoWidth = TRUE,
                          scrollX = TRUE,
                          rownames= TRUE,
                          scrollY = '450px'))
```


```{r}
library(genekitr)
library(DT)
```

### Get gene information => `genInfo`

Support many organisms and three main gene ID types ("symbol", "entrezid" and "ensembl")

Firstly, we take human genes as opening...

Use symbol ID (function could detect fake ID, here is "FAKEID")
```{r}
id = c("MCM10", "CDC20","S100A9", "FOXM1", "KIF23", "MMP1", "CDC45",  "BCC7", "FAKEID", "TP53",'HBD')
info = genInfo(id,org = 'hg')
datatable(info)
```

It is common for one type of gene matched to many results in another type. For example,
according to the message above, we got two matched result for gene "HBD".

If we just want to get one-to-one match, we just need to set `unique=TRUE`

```{r}
info2 = genInfo(id,org = 'hg',unique=TRUE)
identical(id,info2$input_id)
datatable(info2)
```








